### 2024-04-22 scripts/02-data_cleaning.qmd
update pockect area file

# Change the name of the raw data into the clean data
cleaned_pocket_area_data <-
  clean_names(pocket_area_data)

# Select the rows of interest
cleaned_pocket_area_data <-
  cleaned_pocket_area_data |>
  select(
    updated_style,
    group,
    price_group,
    pocket_area
  )

cleaned_pocket_area_data
```

@@

# Change from json format to csv
csv_file <- here::here("data/analysis_data/cleaned_pocket_area_data.csv")

# Write the cleaned data frame to a CSV file
write_csv(cleaned_pocket_area_data, csv_file)
```

>>>>

# Change the name of the raw data into the clean data
cleaned_area_data <-
  clean_names(pocket_area_data)

# Select the rows of interest
cleaned_area_data <-
  cleaned_area_data |>
  select(
    brand,
    style,
    men_women,
    pocket_area,
    price,
  )

cleaned_area_data
```

@@

# Change from json format to csv
csv_file <- here::here("data/analysis_data/cleaned_area_data.csv")

# Write the cleaned data frame to a CSV file
write_csv(cleaned_area_data, csv_file)
```
